Graph Generators: State of the Art and Open Challenges

### 2019-06-11 main.tex
title changed

% Page heads
\markboth{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr}{Modern Graph Generators: A Survey}

% Title portion
%\title{Graph Data Generators in the World of Big Data}
\title{Modern Graph Generators: A Survey}
\author{
ANGELA BONIFATI
\affil{Lyon 1 University, France}
IRENA HOLUBOV\'{A}
\affil{Charles University, Prague, Czech Republic}
ARNAU PRAT-P\'{E}REZ
\affil{DAMA-UPC, Universitat Polit\`ecnica de Catalunya, Spain}
SHERIF SAKR
\affil{University of Tartu, Estonia}
}
% NOTE! Affiliations placed here should be for the institution where the
%       BULK of the research was done. If the author has gone to a new
%       institution, before publication, the (above) affiliation should NOT be changed.
%       The authors 'current' address may be given in the "Author's addresses:" block (below).
%       So for example, Mr. Abdelzaher, the bulk of the research was done at UIUC, and he is
%       currently affiliated with NASA.

@@

This survey provides a comprehensive overview of the state-of-the-art
modern graph generators by focusing on those that are pertinent and
suitable for several data-intensive tasks. Finally, we discuss open
challenges and missing requirements of current graph generators along with their future extensions to new emerging fields.
\end{abstract}

>>>>

% Page heads
\markboth{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr}{Graph Generators: State of the Art and Open Challenges}

% Title portion
%\title{Graph Data Generators in the World of Big Data}
%\title{Modern Graph Generators: A Survey}
\title{Graph Generators: State of the Art and Open Challenges}
\author{
ANGELA BONIFATI
\affil{Lyon 1 University, France}
IRENA HOLUBOV\'{A}
\affil{Charles University, Prague, Czech Republic}
ARNAU PRAT-P\'{E}REZ
\affil{DAMA-UPC, Universitat Polit\`ecnica de Catalunya, Spain}
SHERIF SAKR
\affil{University of Tartu, Estonia}
}
% NOTE! Affiliations placed here should be for the institution where the
%       BULK of the research was done. If the author has gone to a new
%       institution, before publication, the (above) affiliation should NOT be changed.
%       The authors 'current' address may be given in the "Author's addresses:" block (below).
%       So for example, Mr. Abdelzaher, the bulk of the research was done at UIUC, and he is
%       currently affiliated with NASA.

@@

This survey provides a comprehensive overview of the state-of-the-art
graph generators by focusing on those that are pertinent and
suitable for several data-intensive tasks. Finally, we discuss open
challenges and missing requirements of current graph generators along with their future extensions to new emerging fields.
\end{abstract}
